Usability of Mobile Map Applications

### 2014-09-25 usability-study/usability-study.tex
change bolded results to italicized
heuristic evaluation

\section{Usability Metrics}
\subsection{Efficiency}
\par
\textbf{First Task: }Drop a pin on the map and get driving directions to that pin.
\vspace{-.4in}
\begin{figure}[ht]
\begin{center}
\vspace{-.1in}
\includegraphics[keepaspectratio, width=.8\textwidth ]{task1.pdf}
\end{center}
\end{figure}
\begin{center}
\vspace{-.6in}
\par
Average time for task \#1 on Apple Maps app: approx. \textbf{19 seconds}
\par
Average time for task \#1 on Google Maps app: approx. \textbf{21 seconds}
\end{center}
\par
\noindent
This task's results suggest that users are more efficient using Apple Maps. \footnote{Though subjects using Apple Maps were more efficient \textit{on average}, it is important to note that there were a couple of anomalies within the set of Google Maps users.}
\medskip
\medskip
\par
\noindent
\textbf{Second Task: }Find the location of the nearest Vons.
\begin{figure}[ht]
\begin{center}
\vspace{-.5in}
\includegraphics[keepaspectratio, width=.8\textwidth ]{task2.pdf}
\end{center}
\end{figure}
\begin{center}
\vspace{-.6in}
\par
Average time for task \#2 on Apple Maps app: approx. \textbf{24 seconds}
\par
Average time for task \#2 on Google Maps app: approx. \textbf{21 seconds}
\end{center}
\par
\noindent
This task's results suggest that users are more efficient using Google Maps. 
\medskip
\medskip
\par
\noindent
\textbf{Third Task: }Find the fastest route from the current location to LACMA.
\begin{figure}[ht]
\begin{center}
\vspace{-.4in}
\includegraphics[keepaspectratio, width=.8\textwidth ]{task3.pdf}
\end{center}
\end{figure}
\begin{center}
\vspace{-.4in}
\par
Average time for task \#3 on Apple Maps app: approx. \textbf{36 seconds}
\par
Average time for task \#3 on Google Maps app: approx. \textbf{17 seconds}
\end{center}
\par
\noindent
This task's results suggest that users are more efficient using Google Maps.

@@

\subsection{Satisfaction}
\begin{figure}[ht]
\begin{center}
\vspace{-.6in}
\includegraphics[keepaspectratio, width=.8\textwidth ]{satisfaction.pdf}
\end{center}
\end{figure}
\par
\vspace{-.4in}
Satisfaction ratings were on a scale from 1 to 10.
\par
Average rating for Apple Maps: approx. \textbf{6.18}
\par
Average rating for Google Maps: approx. \textbf{7.72}

\begin{multicols}{2}
[
\section{Heuristic Evaluation}
All human things are subject to decay. And when fate summons, Monarchs must obey.
]
Hello, here is some text without a meaning.  This text should show what 
a printed text will look like at this place.
If you read this text, you will get no information.  Really?  Is there 
no information?  Is there
\end{multicols}
\clearpage
\begin{thebibliography}{100} % 100 is a random guess of the total number of 
%references
\bibitem{Nielsen} Nielsen, Jakob, \emph{Usability Engineering}, Boston: Academic, 1993.
\bibitem{Mossberg} Mossberg, Walt., ``The iPhone Takes to the Big Screen," \emph{The Wall Street Journal}, September 2012.
\bibitem{ComScore}``Analytics for a Digital World - ComScore, Inc." \emph{ComScore,Inc}, 2012.
\bibitem{HK} Kopka, H., Daly P.W., \emph{A Guide to LaTeX},
Addison-Wesley, Reading, MA, 1999.
\bibitem{Pan} Pan, D., ``A Tutorial on MPEG/Audio Compression," \emph{IEEE 
Multimedia}, Vol.2, pp.60-74, Summer 1998.
\end{thebibliography}
%%%%%%%%%%%%% end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\section{Usability Metrics}
\subsection{Efficiency}
\par
\textbf{First Task: }Drop a pin on the map and get driving directions to that pin.
\vspace{-.4in}
\begin{figure}[ht]
\begin{center}
\vspace{-.1in}
\includegraphics[keepaspectratio, width=.8\textwidth ]{task1.pdf}
\end{center}
\end{figure}
\begin{center}
\vspace{-.6in}
\par
Average time for task \#1 on Apple Maps app: approx. \textit{19 seconds}
\par
Average time for task \#1 on Google Maps app: approx. \textit{21 seconds}
\end{center}
\par
\noindent
This task's results suggest that users are more efficient using Apple Maps. \footnote{Though subjects using Apple Maps were more efficient \textit{on average}, it is important to note that there were a couple of anomalies within the set of Google Maps users.}
\medskip
\medskip
\par
\noindent
\textbf{Second Task: }Find the location of the nearest Vons.
\begin{figure}[ht]
\begin{center}
\vspace{-.5in}
\includegraphics[keepaspectratio, width=.8\textwidth ]{task2.pdf}
\end{center}
\end{figure}
\begin{center}
\vspace{-.6in}
\par
Average time for task \#2 on Apple Maps app: approx. \textit{24 seconds}
\par
Average time for task \#2 on Google Maps app: approx. \textit{21 seconds}
\end{center}
\par
\noindent
This task's results suggest that users are more efficient using Google Maps. 
\medskip
\medskip
\par
\noindent
\textbf{Third Task: }Find the fastest route from the current location to LACMA.
\begin{figure}[ht]
\begin{center}
\vspace{-.4in}
\includegraphics[keepaspectratio, width=.8\textwidth ]{task3.pdf}
\end{center}
\end{figure}
\begin{center}
\vspace{-.4in}
\par
Average time for task \#3 on Apple Maps app: approx. \textit{36 seconds}
\par
Average time for task \#3 on Google Maps app: approx. \textit{17 seconds}
\end{center}
\par
\noindent
This task's results suggest that users are more efficient using Google Maps.

@@

\subsection{Satisfaction}
\begin{figure}[ht]
\begin{center}
\includegraphics[keepaspectratio, width=.8\textwidth ]{satisfaction.pdf}
\end{center}
\end{figure}
\par
Satisfaction ratings were on a scale from 1 to 10.
\par
Average rating for Apple Maps: approx. \textit{6.18}
\par
Average rating for Google Maps: approx. \textit{7.72}

\begin{multicols}{2}
[
\section{Heuristic Evaluation}
Though usability metrics are extremely important in assessing a system, it is also important to heuristically evaluate systems in order to explore \textit{why} they performed the way they do.
My heuristic evaluations of the mobile map applications will be based on the guidelines documents that correspond to the applications. I will examine Google Maps first.
]
The icons of the Google Maps mobile application comply with the Google Design Guidelines\cite{Google}: simple, modern, geometric in execution, and with rounded corners. Be that as it may, Google Maps completely fails to use any standard iOS icons. Though it is not required to use these provided iOS icons, the iOS Human Interface Guidelines state that it is "a good idea to use the built-in icons as much as possible because users already know what they mean".\cite{Apple}
\includegraphics[width=.45\textwidth]{ios-bar-icons.png}
\includegraphics[width=.5\textwidth]{google-maps.png}

\end{multicols}
\clearpage
\begin{thebibliography}{100} % 100 is a random guess of the total number of 
%references
\bibitem{Nielsen} Nielsen, Jakob, \emph{Usability Engineering}, Boston: Academic, 1993.
\bibitem{Mossberg} Mossberg, Walt., ``The iPhone Takes to the Big Screen," \emph{The Wall Street Journal}, September 2012.
\bibitem{ComScore}``Analytics for a Digital World - ComScore, Inc." \emph{ComScore,Inc}, 2012.
\bibitem{Google} \emph{Material Design}, www.google.com/design/spec/material-design.
\bibitem{Apple} \emph{iOS Human Interface Guidelines}, https://developer.apple.com/library/ios/documentation/userexperience.
\end{thebibliography}
%%%%%%%%%%%%% end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
